\section{Objectives achieved}

The objectives we set during our first meeting were mainly this three:

\begin{itemize}

\item
Build an RESTful API wrapper around EPCON's API with user authentication and persistent data
\item 
Build a web client with focus on user experience and performance
\item 
Build a mobile client with focus on user experience and performance

\end{itemize}

Our project was ambitious, we were 11 students from different countries and communicating in English (which for most of us, including myself, was not our native language), some more experienced than others in terms of working remotely, agile methodology and software development.
\\ \\
We successfully developed the REST API with persistent data and an authentication system and the two clients (web and Android). As of this moment, there are still bugs and issues to work on and the Android app was not yet released on the Google Play Store. Nevertheless, I think we mostly achieved the objectives we have defined at the beginning of the project.

\section{Limitations and future work}

During the execution and development of this project we have faced multiple challenges, some more with more impact than others. Here are some issues we have faced:

\begin{itemize}

\item
Cultural differences between team members
\item 
Working remotely on different time-zones
\item 
Experience gap in terms of agile software development

\end{itemize}

Most of the difficulties we faced were related to team-work issues. All of us were working remotely, in different countries, some in a very different time-zone which created barriers of communication. Another issue we faced was very different ranges of technical knowledge in software development tools and processes. Some of our team members were not familiar with popular programming languages like Java or JavaScript, others had not yet been introduced to versioning tools like Git and most were not familiar with the processes that software development takes, like writing user-stories, following a backlog and working following agile methods.
\\ \\
We have recently published all our code with a permissive open source license on GitHub. So, as of today anyone in the world can start contributing for the project. We plan on continuing to develop the system until September, where our main focus will be on finishing the Android app and bug fixing some issues on the server and on the web client.

\section{Final assessment}

Having the opportunity to work on this project was a pleasure for me. It strengthened my knowledge both in a technical perspective and a team-work related view. I've learned a lot about APIs and the Android SDK and working with such a culturally diverse team made me rethink on how much communication is important.
\\ \\
I feel that EPCON was appreciative of our work and recognized our efforts and in the end we effectively build a tool that was asked for us. Overall it was an amazing experience that I think everyone will take some knowledge home.