% !TEX encoding = UTF-8 Unicode

\pagenumbering{arabic}

The proposed challenge by EPCON was to develop on top of an already existing system that uses AI technology to help doctors and other healthcare workers screen patients in risk of contracting TB. This project from EPCON was focused on computer-aided diagnosis, specifically for tuberculosis, and for under-developed world regions.

\section{Organization description}

EPCON is a small startup company based in Antwerp, Belgium that since 2018 focuses on identifying, monitoring and evaluating epidemic outbreak regions and finding those in need of help through technology and innovation.
\\ \\
Through their partner network, that consists of a vast list of international companies, NGOs and local communities that have proven track records and unique expertise in the field of GIS, AI and healthcare, they consolidate expertise in terms of health data and commit to further innovate and develop technologies to help epidemic control and fight against TB.
\\ \\
By doing this, they aggregate real-time data and combine it with contextual geographical information like population density, disease co-infection indexes, migration ratios and others. And then, using their distributed Bayesian reasoning models, they analyse cause-effect patterns and use neural networks to screen chest x-rays at large scale for computer-aided diagnostics. \cite{EPCON}

\section{Problem description}

One of the already built technologies of EPCON consists of a small web application that connects to their internal API allowing users to upload a chest x-ray photo and receiving a computer generated estimation on how likely is the x-ray to indicate that the patient could have tuberculosis.
\\ \\
After some testing with real doctors in developing countries, EPCON asked the users for some feedback about the usability of the application and they replied with some issues that concerned their use of it.
\\ \\
One of the biggest complaints was referent to the upload process of the photos of x-rays where the process was taking too long and when the connection was unstable it would fail the request and stop uploading.
\\ \\
The objective was to build a wrapper system around EPCON's machine learning API to provide users with a better experience, performance and increased features. So, the main goals of this project were:

\begin{itemize}

\item
Build an RESTful API wrapper around EPCON's API with user authentication and persistent data
\item 
Build a web client with focus on user experience and performance
\item 
Build a mobile client with focus on user experience and performance

\end{itemize}

\section{Approach}

We were 11 students from 7 different countries working together remotely for approximately 3 months. We have a first initial meeting during one week in Belgium where we had the chance to meet each other, to get to know the people behind the company and to be elucidated about more specific details on the project we were about to develop.


\section{Contributions}

The main beneficiaries from the development of this project would be the local communities in developing countries where the tuberculosis incidence is still very high and where EPCON mostly focuses their efforts. EPCON uses their technologies and expertise in function of health and commit themselves to further innovate and develop technologies in function of epidemic control and the fight against tuberculosis.
\\ \\
In order to do so, they partner up with some third parties like RiskScape, in Johannesburgm South Africa, which combines spatial analysis and risk modelling to identify unique locations and make them addressable \cite{RiskScape}, CognitiveSystems, located in Cape Town, also in South Africa, where they work with biologically inspired computing \cite{CognitiveSystems} and Imec, in Belgium, where people work to bring advanced diagnostics and precision medicine \cite{Imec}. Imec was also the startup company which provided the space and material for our first meeting in Belgium.
\\ \\
EPCON also parters up with some NGOs like the Stop TB Partership where under their guidance they follow international standards on quality, best practices and sustainability and partner with the public and private sector to ensure interoperability and a patient centric approach in the fight against tuberculosis \cite{StopTBPartnership}.

\section{Work planning}

We decided to have a weekly meeting, every Thursday at 20:00 CET using an online video-conference platform provided to us by the company. Where we discussed all the topics and issues we had during the previous week and all the tasks and user stories we were about to develop on the next week. Vincent, the CEO of EPCON, would join this meeting every two weeks.
\\ \\
In order to communicate with each other we used Slack as it had a free-tier option and it allowed us to communicate, send files and make voice calls.
\\ \\
To manage our workflow and write down all the user stories and their respective status we decided to use Trello, a web-based Kanban-style list-making application. \cite{Trello} We first thought about using Jira, an agile project management software developed by Atlassian, but, as we had some team members who were not very experienced with scrum-based workflow and software development in general, we decided to go with Trello as it seemed a much more simpler, user-friendly option which could fulfill all our organizational needs.
\\ \\
In order to build software in a continuous development fashion we need a version control system where we could track version changes of our code repository. Nowadays, it is almost industry standard to use Git as a version control software, but there are other options like Mercurial or SVN, so we decided to use Git. As a Git platform we used GitLab, as it offered free private repositories and free CI/CD tools.

\section{Technologies used}

As described in the previous sections, to the development of this project it was necessary to use different frameworks, technologies and tools related to team work and software development. Here is a detailed list of each of them:
\\

\textbf{Programming languages:}

\begin{itemize}
\item
Node.js
\item
JavaScript
\item 
HTML
\item 
CSS
\item 
Kotlin
\item 
Java
\item 
Bash
\end{itemize}

\\ \\

\textbf{Frameworks:}

\begin{itemize}
\item
React
\item 
Express
\item 
Bootstrap
\end{itemize}

\\ \\

\textbf{Software:}

\begin{itemize}
\item
Visual Studio
\item 
Postman
\item 
Visual Paradigm
\end{itemize}

\\ \\

\textbf{Tools:}

\begin{itemize}
\item
Trello
\item 
Google Drive
\item 
Slack
\item 
Zoom
\end{itemize}

\\
These were the technologies that helped the development of the project in a sustainable way. It is important to note that all technologies, frameworks and tools were defined at the first meeting in Belgium.
